Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
typo

The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g. the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$. The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.

>>>>

The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g. the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u')_y \geq L(u)_y + \inprod{v}{u'-u}$ for all $u'$.} of $L$ at these embedding points.
To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
In particular, we use heavily that a convex function is minimized at a point if and only if the origin $\vec{0}$ is in its subgradient set at that point.
